### 2024-01-16 paper/main.tex
testing figures
committing paper
checking out figures
all figures in there, not quite done tho

\documentclass[12pt,letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{fontspec} %XeLatex
\usepackage{soul,xcolor}
\usepackage{graphicx,wrapfig}
% \usepackage[backend=biber]{biblatex}
\usepackage[paper=letterpaper,
            %includefoot, % Uncomment to put page number above margin
            marginparwidth=0.0in,     % Length of section titles
            marginparsep=.05in,       % Space between titles and text
            margin=1.0in,               % 1 inch margins
            includemp]{geometry}
\usepackage{fontspec} %XeLatex
\setmainfont{AvenirLTProBook.otf}[
    Path =fonts/,
    BoldFont = AvenirNextLTProBold.otf,
    %BoldFont = AvenirLTProHeavy.otf, % another option for bold font
    ItalicFont = AvenirLTProBookOblique.otf,
    BoldItalicFont = AvenirLTProHeavyOblique.otf
]
% \definecolor{myudblue}{RGB}{0, 83, 159}
\begin{document}
HELLOOOOOOOOO

aw;lesfajfp 8uyf

% \begin{figure}
%     \centering
%     \includegraphics{/figures/test.png}
% \end{figure}

>>>>

\documentclass[12pt,letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{fontspec} %XeLatex
\usepackage{soul,xcolor}
\usepackage{graphicx,wrapfig}
\usepackage{float}
\graphicspath{ {./figures/} }
% \usepackage[backend=biber]{biblatex}
\usepackage[paper=letterpaper,
            %includefoot, % Uncomment to put page number above margin
            marginparwidth=0.0in,     % Length of section titles
            marginparsep=.05in,       % Space between titles and text
            margin=1.0in,               % 1 inch margins
            includemp]{geometry}
\usepackage{fontspec} %XeLatex
\setmainfont{AvenirLTProBook.otf}[
    Path =fonts/,
    BoldFont = AvenirNextLTProBold.otf,
    %BoldFont = AvenirLTProHeavy.otf, % another option for bold font
    ItalicFont = AvenirLTProBookOblique.otf,
    BoldItalicFont = AvenirLTProHeavyOblique.otf
]
\newcommand{\SethCaption}[2]{\noindent\textbf{\textcolor{black}{#1}} {#2}}
\newcommand{\SectionHeader}[1]{\noindent\textbf{\Large{\textcolor{black}{#1}}}\normalsize }
\newcommand{\SubSectionHeader}[1]{\noindent\Large{\textcolor{black}{#1}}\normalsize }

% \definecolor{myudblue}{RGB}{0, 83, 159}
\begin{document}
\SectionHeader{Main Figures}

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{figures/exp1_experimental_design.png}

    \SethCaption{Figure 1.}{Experimental Design}
\end{figure}
\begin{figure}[H]
    \centering
    \includegraphics[scale =1]{figures/exp1_movement_onset_panel.png}

    \SethCaption{Figure 2.}{Data}
\end{figure}
\begin{figure}[H]
    \centering
    \includegraphics[scale = 1]{figures/exp1_score_metrics_panel.png}

    \SethCaption{Figure 3.}{Data}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[scale = 1]{figures/model_diagram.png}

    \SethCaption{Figure 4.}{Data}
\end{figure}
\begin{figure}[H]
    \centering
    \includegraphics[scale = 1]{figures/exp1_data_panel_with_models.png}

    \SethCaption{Figure 5.}{Data w/ models}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[scale = 1]{figures/exp2_design.png}

    \SethCaption{Figure 6.}{Experiment 2 Design}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[scale = 1]{figures/exp2_reaction_panel.png}

    \SethCaption{Figure 7.}{React or Guess panel}
\end{figure}
